<<<<<<< HEAD
=======
---
title: "Week 2 Report"
author: "Giles Carlos, Alyssandrei Parinas, Cadence Pinkerton, James Owens, Mia Chiu"
date: '2022-07-01'
output: html_document
---

# Libraries

```{r}
#install.packages("runner")

library(tidyverse)
library(R.matlab)
library(janitor)
library(readr)
library(dplyr)
library(runner)
library(gridExtra)
```

# Loading in Data

```{r}
#behavior_m <- readMat(here::here("data/superchris_BM.mat"))
#ensemble_m <- readMat(here::here("data/superchris_EM_onlyspikes_c.mat"))
#behavior_info <- readMat(here::here("data/behav_info.mat"))
# package can't load this version of matlab files
# ensemble_mat <- readMat(here::here("data/SuperChris_EnsembleMatrix.mat"))
```


# Cleaning Data


### Pulling from List

```{r}
em <- data.frame(ensemble_m[1])
bm <- data.frame(behavior_m[1]) 
col_names <- data.frame(behavior_m[2])
```

### Renaming variables 

```{r}
  bm <-
    bm %>%
     rename(time_bin = behavMatrix.1,
         odor_1 = behavMatrix.2,
         odor_2 = behavMatrix.3,
         odor_3 = behavMatrix.4,
         odor_4 = behavMatrix.5,
         odor_5 = behavMatrix.6,
         position_1 = behavMatrix.7,
         position_2 = behavMatrix.8,
         position_3 = behavMatrix.9,
         position_4 = behavMatrix.10,
         position_5 = behavMatrix.11,
         in_seq_log = behavMatrix.12,
         performance_log = behavMatrix.13,
         poke_events = behavMatrix.14,
         front_reward = behavMatrix.15,
         back_reward = behavMatrix.16,
         x_val_pos = behavMatrix.17,
         y_val_pos = behavMatrix.18)
  
  bm <- clean_names(bm)
  
  em <- 
    em %>%
     rename(neuron_1 = EM.1,
            neuron_2 = EM.2,
            neuron_3 = EM.3,
            neuron_4 = EM.4,
            neuron_5 = EM.5,
            neuron_6 = EM.6,
            neuron_7 = EM.7,
            neuron_8 = EM.8,
            neuron_9 = EM.9,
            neuron_10 = EM.10,
            neuron_11 = EM.11,
            neuron_12 = EM.12,
            neuron_13 = EM.13,
            neuron_14 = EM.14,
            neuron_15 = EM.15,
            neuron_16 = EM.16,
            neuron_17 = EM.17,
            neuron_18 = EM.18,
            neuron_19 = EM.19,
            neuron_20 = EM.20,
            neuron_21 = EM.21,
            neuron_22 = EM.22,
            neuron_23 = EM.23,
            neuron_24 = EM.24,
            neuron_25 = EM.25,
            neuron_26 = EM.26,
            neuron_27 = EM.27,
            neuron_28 = EM.28,
            neuron_29 = EM.29,
            neuron_30 = EM.30,
            neuron_31 = EM.31,
            neuron_32 = EM.32,
            neuron_33 = EM.33,
            neuron_34 = EM.34,
            neuron_35 = EM.35,
            neuron_36 = EM.36,
            neuron_37 = EM.37,
            neuron_38 = EM.38,
            neuron_39 = EM.39,
            neuron_40 = EM.40,
            neuron_41 = EM.41,
            neuron_42 = EM.42,
            neuron_43 = EM.43,
            neuron_44 = EM.44,
            neuron_45 = EM.45,
            neuron_46 = EM.46,
            neuron_47 = EM.47)
  
  em <- clean_names(em)
```

### changing variable types

```{r}
 range(bm$time_bin) # could use min or max function
  unique(bm$odor_5)  
  unique(bm$position_5) 
  unique(bm$in_seq_log) 
  unique(bm$performance_log) 
  unique(bm$poke_events) 
  unique(bm$front_reward) 
  unique(bm$back_reward) 
  table(bm$performance_log)
  
  bm <-
    bm %>%
    mutate(odor_1 = as.integer(odor_1),
           odor_2 = as.integer(odor_2),
           odor_3 = as.integer(odor_3),
           odor_4 = as.integer(odor_4),
           odor_5 = as.integer(odor_5),
           position_1 = as.integer(position_1),
           position_2 = as.integer(position_2),
           position_3 = as.integer(position_3),
           position_4 = as.integer(position_4),
           position_5 = as.integer(position_5),
           in_seq_log = as.integer(in_seq_log),
           performance_log = as.integer(performance_log),
           poke_events = as.integer(poke_events),
           front_reward = as.integer(front_reward),
           back_reward = as.integer(back_reward))
  glimpse(bm)
```

# Get In-Sequence Correct Trials

```{r}
# indices for each odor
idx_1 <- which(behavior_info$preTrialBehavMatrix[seq(3, length(behavior_info$preTrialBehavMatrix), 15)] == 1, arr.ind = TRUE)
idx_2 <- which(behavior_info$preTrialBehavMatrix[seq(3, length(behavior_info$preTrialBehavMatrix), 15)] == 2, arr.ind = TRUE)
idx_3 <- which(behavior_info$preTrialBehavMatrix[seq(3, length(behavior_info$preTrialBehavMatrix), 15)] == 3, arr.ind = TRUE)
idx_4 <- which(behavior_info$preTrialBehavMatrix[seq(3, length(behavior_info$preTrialBehavMatrix), 15)] == 4, arr.ind = TRUE)
idx_5 <- which(behavior_info$preTrialBehavMatrix[seq(3, length(behavior_info$preTrialBehavMatrix), 15)] == 5, arr.ind = TRUE)

all_trials <- list(idx_1, idx_2, idx_3, idx_4, idx_5)
names(all_trials) <- c("odor_1", "odor_2", "odor_3", "odor_4", "odor_5")

# Odor 1
selected_performance <- behavior_info$preTrialBehavMatrix[seq(6, length(behavior_info$preTrialBehavMatrix), 15)][idx_1]
selected_durations <- behavior_info$preTrialBehavMatrix[seq(5, length(behavior_info$preTrialBehavMatrix), 15)][idx_1]
selected_positions <- behavior_info$preTrialBehavMatrix[seq(4, length(behavior_info$preTrialBehavMatrix), 15)][idx_1]

for (i in 1:length(idx_1)) {
  if (selected_performance[i] == 0 & selected_positions[i] == 1 & selected_durations[i] > 1.05) {
    idx_1[i] <- idx_1[i]
  } else if (selected_performance[i] == 1 & selected_positions[i] == 1) {
    idx_1[i] <- idx_1[i] 
  } else {
    idx_1[i] <- NA
  }
}

all_trials$odor_1 <- idx_1[!is.na(idx_1)]
```

```{r}
# all_trials <- list()
# 
# all_trials[[1]] <- which(bm$odor_1 == 1 & bm$position_1 == 1 & bm$performance_log == 1, arr.ind = TRUE)
# 
# all_trials[[2]] <- which(bm$odor_2 == 1 & bm$position_2 == 1 & bm$performance_log == 1, arr.ind = TRUE)
# 
# all_trials[[3]] <- which(bm$odor_3 == 1 & bm$position_3 == 1 & bm$performance_log == 1, arr.ind = TRUE)
# 
# all_trials[[4]] <- which(bm$odor_4 == 1 & bm$position_4 == 1 & bm$performance_log == 1, arr.ind = TRUE)
# 
# all_trials[[5]] <- which(bm$odor_5 == 1 & bm$position_5 == 1 & bm$performance_log == 1, arr.ind = TRUE)
```


# Merging Ensemble Matrix and Behavior Matrix by Odor 

```{r}
bm_odor_1 <- 
  bm %>% 
  select(time_bin, odor_1)

bm_odor_1 <- 
  cbind(bm_odor_1, em) %>% 
  filter(odor_1 == 1)


bm_odor_2 <- 
  bm %>% 
  select(time_bin, odor_2)

bm_odor_2 <- 
  cbind(bm_odor_2, em) %>% 
  filter(odor_2 == 1)

bm_odor_3 <- 
  bm %>% 
  select(time_bin, odor_3)

bm_odor_3 <- 
  cbind(bm_odor_3, em) %>% 
  filter(odor_3 == 1)

bm_odor_4 <- 
  bm %>% 
  select(time_bin, odor_4)

bm_odor_4 <- 
  cbind(bm_odor_4, em) %>% 
  filter(odor_4 == 1)

bm_odor_5 <- 
  bm %>% 
  select(time_bin, odor_5)

bm_odor_5 <- 
  cbind(bm_odor_5, em) %>% 
  filter(odor_5 == 1)

```

# Adding Trial Column in Behavior Matrix

```{r}
bm_trials <- bm %>% 
  select(time_bin, odor_1, poke_events) %>% 
  filter(poke_events != 0) %>% 
  mutate(poke_events = case_when(poke_events != 0 ~ 1,
                                 poke_events == 0 ~ 0)) %>% 
  mutate(trial = as.integer(ceiling(cumsum(poke_events) / 2))) %>% 
  select(time_bin, trial) 

bm <- bm %>% 
  left_join(bm_trials, by = c("time_bin")) 
  
bm_trials %>% 
  tail()

# Filling in gaps between trial start and trial end
bm <- bm %>% 
  mutate(trial = runner::fill_run(trial, only_within = TRUE)) %>% 
  replace_na(list(trial = 0))
```

# Merging Trials and Time with Ensemble Matrix (Neurons)

```{r}
em_trials <- bm %>% 
  select(time_bin, trial, odor_1, odor_2, odor_3, odor_4, odor_5) %>% 
  cbind(em) 
```



```{r}
poke_indices <- which(bm$poke_events == 1, arr.ind = T)

neuron <- ncol(em)
window_size <- 2000

time <- window_size*2
trials <- length(poke_indices)

em_trial <- array(NA, dim = c(time, neuron, trials))

for (i in 1:length(poke_indices)) {
  em_trial[,,i] <- as.matrix(em[(poke_indices[i]-window_size):((poke_indices[i]+window_size)-1),])
}

trial_sums <- rowSums(em_trial, dims = 2)

plot(trial_sums[,3], type = "l") 
```


# Exploratory Data Analysis

### Neurons Firing Bar Plot

```{r fig.width = 10}
firing_counts <- em %>% 
  colSums()

data.frame(neuron = factor(names(firing_counts)), 
           firing_counts) %>%
  arrange(desc(firing_counts)) %>% 
  ggplot(aes(reorder(neuron, -firing_counts), firing_counts)) + 
  geom_col() +
  labs(title = "Session Spike Counts", 
       x = "Neuron", 
       y = "Number of Spikes") +
  theme(axis.text.x = element_text(angle = 90, 
                                   vjust = 0.5, 
                                   hjust = 1))
```

### Raster Plot Displaying How Neurons Fire Over Time

```{r}
which(em == 1, arr.ind = TRUE) %>% 
  as.data.frame() %>% 
  ggplot(aes(x = row, y = col)) +
  geom_point(shape = 0, size = 0.001) +
  scale_x_continuous(labels = scales::comma) +
  labs(title = "Raster Plot", 
       x = "Time (ms)",
       y = "Neuron Number")

which(em == 1, arr.ind = TRUE) %>% 
  as.data.frame() %>% 
  filter(row < 100000) %>% 
  ggplot(aes(x = row, y = col)) +
  geom_point(shape = 0, size = 0.001) +
  scale_x_continuous(labels = scales::comma) +
  labs(title = "Raster Plot with Shorter Duration", 
       x = "Time (ms)",
       y = "Neuron Number")
```

### Exploring Neuron 2

__Examining Firing Patterns Over Sequences of Trials Using Raster Plot__

```{r fig.height = 3}
em_trials %>% 
  select(time_bin, trial, neuron_2) %>% 
  filter(trial != 0 & neuron_2 == 1)

em_trials %>% 
  select(time_bin, trial, neuron_2) %>% 
  filter(trial != 0 & neuron_2 == 1) %>% 
  group_by(trial) %>% 
  mutate(time_bin = time_bin - min(time_bin)) %>% 
  ggplot(aes(x = time_bin, y = trial, z = neuron_2)) +
  geom_point(shape = 0, size = 1) +
  scale_y_discrete(limits = c("1":"250")) +
  labs(x = "Time (MS)", 
       y = "Trial Number", 
       title = "Neuron 2 Firing Across Trials") +
  theme(legend.position = "none", 
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

em_trials %>% 
  select(time_bin, trial, neuron_2) %>% 
  filter(trial != 0 & neuron_2 == 1) %>% 
  group_by(trial) %>% 
  mutate(time_bin = time_bin - min(time_bin)) %>% 
  ggplot(aes(x = time_bin)) + 
  geom_histogram(color = "white") +
  labs(x = "Time (MS)",
       y = "Firing Count", 
       title = "Firing Counts of Neuron 2 Throughout Trial Run") 

```

__Examining Firing Patterns Over Sequences of Trials By Odor For Neuron 15__

```{r fig.height = 8, fig.width = 10}
em_trials %>% 
  select(time_bin, trial, neuron_15) %>% 
  filter(trial != 0 & neuron_15 == 1) %>% 
  group_by(trial) %>% 
  mutate(time_bin = time_bin - min(time_bin)) %>% 
  ggplot(aes(x = time_bin)) + 
  geom_histogram(color = "white") +
  labs(x = "Time (MS)",
       y = "Firing Count", 
       title = "Firing Counts of Neuron 15 Throughout Trial Run") 


odor_1_trials <- em_trials %>% 
  filter(odor_1 == 1) %>% 
  select(trial) %>% 
  pull()

odor_2_trials <- em_trials %>% 
  filter(odor_2 == 1) %>% 
  select(trial) %>% 
  pull()

odor_3_trials <- em_trials %>% 
  filter(odor_3 == 1) %>% 
  select(trial) %>% 
  pull()

odor_4_trials <- em_trials %>% 
  filter(odor_4 == 1) %>% 
  select(trial) %>% 
  pull()

odor_5_trials <- em_trials %>% 
  filter(odor_5 == 1) %>% 
  select(trial) %>% 
  pull()

neuron_15_spikes_o1 <- em_trials %>% 
  filter(trial %in% odor_1_trials) %>% 
  select(time_bin, trial, odor_1, neuron_15) %>% 
  group_by(trial) %>% 
  mutate(time_bin = time_bin - min(time_bin)) %>% 
  filter(neuron_15 == 1) %>% 
  ggplot(aes(x = time_bin)) + 
  geom_histogram(color = "white") +
  labs(x = "Time (MS)",
       y = "Firing Count", 
       title = "Firing Counts of Neuron 15 Throughout Trial Run for Odor 1") 



neuron_15_spikes_o2 <- em_trials %>% 
  filter(trial %in% odor_2_trials) %>% 
  select(time_bin, trial, odor_2, neuron_15) %>% 
  group_by(trial) %>% 
  mutate(time_bin = time_bin - min(time_bin)) %>% 
  filter(neuron_15 == 1) %>% 
  ggplot(aes(x = time_bin)) + 
  geom_histogram(color = "white") +
  labs(x = "Time (MS)",
       y = "Firing Count", 
       title = "Firing Counts of Neuron 15 Throughout Trial Run for Odor 2") 

neuron_15_spikes_o3 <- em_trials %>% 
  filter(trial %in% odor_3_trials) %>% 
  select(time_bin, trial, odor_3, neuron_15) %>% 
  group_by(trial) %>% 
  mutate(time_bin = time_bin - min(time_bin)) %>% 
  filter(neuron_15 == 1) %>% 
  ggplot(aes(x = time_bin)) + 
  geom_histogram(color = "white") +
  labs(x = "Time (MS)",
       y = "Firing Count", 
       title = "Firing Counts of Neuron 15 Throughout Trial Run for Odor 3") 

neuron_15_spikes_o4 <- em_trials %>% 
  filter(trial %in% odor_4_trials) %>% 
  select(time_bin, trial, odor_4, neuron_15) %>% 
  group_by(trial) %>% 
  mutate(time_bin = time_bin - min(time_bin)) %>% 
  filter(neuron_15 == 1) %>% 
  ggplot(aes(x = time_bin)) + 
  geom_histogram(color = "white") +
  labs(x = "Time (MS)",
       y = "Firing Count", 
       title = "Firing Counts of Neuron 15 Throughout Trial Run for Odor 4") 

neuron_15_spikes_o5 <- em_trials %>% 
  filter(trial %in% odor_5_trials) %>% 
  select(time_bin, trial, odor_5, neuron_15) %>% 
  group_by(trial) %>% 
  mutate(time_bin = time_bin - min(time_bin)) %>% 
  filter(neuron_15 == 1) %>% 
  ggplot(aes(x = time_bin)) + 
  geom_histogram(color = "white") +
  labs(x = "Time (MS)",
       y = "Firing Count", 
       title = "Firing Counts of Neuron 15 Throughout Trial Run for Odor 5") 

grid.arrange(neuron_15_spikes_o1, 
             neuron_15_spikes_o2, 
             neuron_15_spikes_o3,
             neuron_15_spikes_o4,
             neuron_15_spikes_o5,
             nrow = 2, 
             ncol = 3)

```

__Examining Firing Patterns Over Sequences of Trials By Odor For Neuron 15__


```{r fig.height = 8, fig.width = 10}
neuron_2_spikes_o1 <- em_trials %>% 
  filter(trial %in% odor_1_trials) %>% 
  select(time_bin, trial, odor_1, neuron_2) %>% 
  group_by(trial) %>% 
  mutate(time_bin = time_bin - min(time_bin)) %>% 
  filter(neuron_2 == 1) %>% 
  ggplot(aes(x = time_bin)) + 
  geom_histogram(color = "white") +
  labs(x = "Time (MS)",
       y = "Firing Count", 
       title = "Firing Counts of Neuron 2 Throughout Trial Run for Odor 1") 



neuron_2_spikes_o2 <- em_trials %>% 
  filter(trial %in% odor_2_trials) %>% 
  select(time_bin, trial, odor_2, neuron_2) %>% 
  group_by(trial) %>% 
  mutate(time_bin = time_bin - min(time_bin)) %>% 
  filter(neuron_2 == 1) %>% 
  ggplot(aes(x = time_bin)) + 
  geom_histogram(color = "white") +
  labs(x = "Time (MS)",
       y = "Firing Count", 
       title = "Firing Counts of Neuron 2 Throughout Trial Run for Odor 2") 

neuron_2_spikes_o3 <- em_trials %>% 
  filter(trial %in% odor_3_trials) %>% 
  select(time_bin, trial, odor_3, neuron_2) %>% 
  group_by(trial) %>% 
  mutate(time_bin = time_bin - min(time_bin)) %>% 
  filter(neuron_2 == 1) %>% 
  ggplot(aes(x = time_bin)) + 
  geom_histogram(color = "white") +
  labs(x = "Time (MS)",
       y = "Firing Count", 
       title = "Firing Counts of Neuron 2 Throughout Trial Run for Odor 3") 

neuron_2_spikes_o4 <- em_trials %>% 
  filter(trial %in% odor_4_trials) %>% 
  select(time_bin, trial, odor_4, neuron_2) %>% 
  group_by(trial) %>% 
  mutate(time_bin = time_bin - min(time_bin)) %>% 
  filter(neuron_2 == 1) %>% 
  ggplot(aes(x = time_bin)) + 
  geom_histogram(color = "white") +
  labs(x = "Time (MS)",
       y = "Firing Count", 
       title = "Firing Counts of Neuron 2 Throughout Trial Run for Odor 4") 

neuron_2_spikes_o5 <- em_trials %>% 
  filter(trial %in% odor_5_trials) %>% 
  select(time_bin, trial, odor_5, neuron_2) %>% 
  group_by(trial) %>% 
  mutate(time_bin = time_bin - min(time_bin)) %>% 
  filter(neuron_2 == 1) %>% 
  ggplot(aes(x = time_bin)) + 
  geom_histogram(color = "white") +
  labs(x = "Time (MS)",
       y = "Firing Count", 
       title = "Firing Counts of Neuron 2 Throughout Trial Run for Odor 5") 

grid.arrange(neuron_2_spikes_o1, 
             neuron_2_spikes_o2, 
             neuron_2_spikes_o3,
             neuron_2_spikes_o4,
             neuron_2_spikes_o5,
             nrow = 2, 
             ncol = 3)

```



```{r}
em_trials %>% 
  select(time_bin, trial, neuron_2) %>% 
  filter(trial != 0 & neuron_2 == 1) %>% 
  ggplot(aes(x = time_bin, y = trial, z = neuron_2, color = as.factor(trial))) +
  geom_point(shape = 0, size = 1) +
  scale_y_discrete(limits = c("1":"250")) +
  labs(x = "Time (MS)", 
       y = "Trial Number", 
       title = "Neuron 2 Firing Across Trials") +
  theme(legend.position = "none", 
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

em_trials %>% 
  select(time_bin, trial, neuron_2) %>% 
  filter(trial > 0 & trial <= 50 & neuron_2 == 1) %>% 
  ggplot(aes(x = time_bin, y = trial, z = neuron_2, color = as.factor(trial))) +
  geom_point(shape = 0, size = 1) +
  scale_y_discrete(limits = c("1":"50")) +
  labs(x = "Time (MS)", 
       y = "Trial Number", 
       title = "Neuron 2 Firing Across Trials (Zoomed In)") +
  theme(legend.position = "none")

em_trials %>% 
  select(time_bin, trial, neuron_2) %>% 
  filter(trial > 0 & trial <= 10 & neuron_2 == 1) %>% 
  ggplot(aes(x = time_bin, y = trial, z = neuron_2, color = as.factor(trial))) +
  geom_point(shape = 0, size = 1) +
  scale_y_discrete(limits = c("1":"10")) +
  labs(x = "Time (MS)", 
       y = "Trial Number", 
       title = "Neuron 2 Firing Across Trials (Zoomed In Even More)")
```

__Examining Firing Patterns of Neuron 2 Using Bar Plots__

```{r}
em_trials %>% 
  select(trial, neuron_2) %>% 
  filter(trial != 0 & neuron_2 == 1) %>% 
  ggplot(aes(x = as.factor(trial))) + 
  geom_bar() +
  theme(legend.position = "none", 
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank())

em_trials %>% 
  select(trial, neuron_2) %>% 
  filter(trial != 0 & neuron_2 == 1) %>% 
  ggplot(aes(x = as.factor(trial))) + 
  geom_bar() +
  scale_x_discrete(limits = c("1":"50"))
  
em_trials %>% 
  select(trial, neuron_2) %>% 
  filter(trial != 0 & neuron_2 == 1) %>% 
  ggplot(aes(x = as.factor(trial))) + 
  geom_bar() +
  scale_x_discrete(limits = c("1":"10"))
```

```{r}
em_trials %>% 
  select(time_bin, trial, neuron_2) %>%
  group_by(trial) %>% 
  count(trial) %>% 
  arrange(desc(n)) %>% 
  rename(firing_count = n) %>% 
  head()
```

Neuron 2 consistently fires across all trials but it also appears to fire when poke event hasn't even occurred. Neuron 2 appears to be firing consistently throughout the whole experiment. 


### Peristimilus Histogram

```{r}
poke_indices <- which(bm$poke_events == 1, arr.ind = T)

neuron <- ncol(em)
window_size <- 2000
time <- window_size*2
trials <- length(poke_indices)

em_trial <- array(NA, dim = c(time, neuron, trials))

for (i in 1:length(poke_indices)) {
  em_trial[,,i] <- as.matrix(em[(poke_indices[i]-window_size):((poke_indices[i]+window_size)-1),])
}

trial_sums <- rowSums(em_trial, dims = 2)
plot(trial_sums[,2], type = "l") 

```







### Poke Events


```{r}
bm %>% 
  select(time_bin, odor_1, poke_events) %>% 
  ggplot(aes(x = time_bin, y = poke_events)) + 
  geom_line() +
  geom_line(aes(x = time_bin, y = odor_1), colour = "Red")

bm %>% 
  select(time_bin, odor_1, odor_2, odor_3, odor_4, odor_5, poke_events) %>% 
  filter(time_bin > 2500 & time_bin < 3000) %>% 
  ggplot(aes(x = time_bin, y = poke_events)) + 
  geom_line() +
  geom_line(aes(x = time_bin, y = odor_1), colour = "Red") +
  geom_line(aes(x = time_bin, y = odor_2), colour = "Orange") +
  geom_line(aes(x = time_bin, y = odor_3), colour = "Green")
  geom_line(aes(x = time_bin, y = odor_4), colour = "Blue")
  geom_line(aes(x = time_bin, y = odor_5), colour = "Purple")

```

### Cells Firing in Odor vs Outside Odor

### Neurons Firing in Certain Positions 

### Odor A

```{r}
odor_a_plot <- bm %>% 
  select(time_bin, odor_1) %>% 
  ggplot(aes(x = time_bin, y = odor_1)) + 
  geom_line() +
  labs(x = "Time",
       y = "Odor A")

odor_a_plot
```

### Odor B

```{r}
odor_b_plot <- bm %>% 
  select(time_bin, odor_2) %>% 
  ggplot(aes(x = time_bin, y = odor_2)) + 
  geom_line()  +
  labs(x = "Time",
       y = "Odor B")

odor_b_plot
```

### Odor C

```{r}
odor_c_plot <- bm %>% 
  select(time_bin, odor_3) %>% 
  ggplot(aes(x = time_bin, y = odor_3)) + 
  geom_line()  +
  labs(x = "Time",
       y = "Odor C")

odor_c_plot
```

### Odor D

```{r}
odor_d_plot <- bm %>% 
  select(time_bin, odor_4) %>% 
  ggplot(aes(x = time_bin, y = odor_4)) + 
  geom_line()  +
  labs(x = "Time",
       y = "Odor D")

odor_d_plot
```

### Odor E

```{r}
odor_e_plot <- bm %>% 
  select(time_bin, odor_5) %>% 
  ggplot(aes(x = time_bin, y = odor_5)) + 
  geom_line()  +
  labs(x = "Time",
       y = "Odor E")

odor_e_plot
```

>>>>>>> e211d2ded1bb688ae2cbec2d3ed388385299024d
