---
title: "Week 3 Report Part 2"
author: "Giles Carlos, Mia Chiu, Alyssandrei Parinas, Cadence Pinkerton, James Owens"
date: '2022-07-12'
output: html_document
---

# Libraries

```{r}
#install.packages("runner")
library(tidyverse)
library(R.matlab)
library(janitor)
library(readr)
library(dplyr)
library(runner)
library(gridExtra)
library(caret)
library(InformationValue)
library(ISLR)
```

# Loading in Data

```{r}
behavior_m <- readMat(here::here("data/superchris_BM.mat"))
ensemble_m <- readMat(here::here("data/superchris_EM_onlyspikes_c.mat"))
```

# Cleaning Data

### Pulling from List

```{r}
em <- data.frame(ensemble_m[1])
bm <- data.frame(behavior_m[1]) 
col_names <- data.frame(behavior_m[2])
```

### Renaming variables 

```{r}
bm <-
  bm %>%
  rename(time_bin = behavMatrix.1,
         odor_1 = behavMatrix.2,
         odor_2 = behavMatrix.3,
         odor_3 = behavMatrix.4,
         odor_4 = behavMatrix.5,
         odor_5 = behavMatrix.6,
         position_1 = behavMatrix.7,
         position_2 = behavMatrix.8,
         position_3 = behavMatrix.9,
         position_4 = behavMatrix.10,
         position_5 = behavMatrix.11,
         in_seq_log = behavMatrix.12,
         performance_log = behavMatrix.13,
         poke_events = behavMatrix.14,
         front_reward = behavMatrix.15,
         back_reward = behavMatrix.16,
         x_val_pos = behavMatrix.17,
         y_val_pos = behavMatrix.18)
  
bm <- clean_names(bm)
  
em <- subset(em, select = -c(EM.1) )

em <- 
  em %>%
  rename(neuron_1 = EM.2,
         neuron_2 = EM.3,
         neuron_3 = EM.4,
         neuron_4 = EM.5,
         neuron_5 = EM.6,
         neuron_6 = EM.7,
         neuron_7 = EM.8,
         neuron_8 = EM.9,
         neuron_9 = EM.10,
         neuron_10 = EM.11,
         neuron_11 = EM.12,
         neuron_12 = EM.13,
         neuron_13 = EM.14,
         neuron_14 = EM.15,
         neuron_15 = EM.16,
         neuron_16 = EM.17,
         neuron_17 = EM.18,
         neuron_18 = EM.19,
         neuron_19 = EM.20,
         neuron_20 = EM.21,
         neuron_21 = EM.22,
         neuron_22 = EM.23,
         neuron_23 = EM.24,
         neuron_24 = EM.25,
         neuron_25 = EM.26,
         neuron_26 = EM.27,
         neuron_27 = EM.28,
         neuron_28 = EM.29,
         neuron_29 = EM.30,
         neuron_30 = EM.31,
         neuron_31 = EM.32,
         neuron_32 = EM.33,
         neuron_33 = EM.34,
         neuron_34 = EM.35,
         neuron_35 = EM.36,
         neuron_36 = EM.37,
         neuron_37 = EM.38,
         neuron_38 = EM.39,
         neuron_39 = EM.40,
         neuron_40 = EM.41,
         neuron_41 = EM.42,
         neuron_42 = EM.43,
         neuron_43 = EM.44,
         neuron_44 = EM.45,
         neuron_45 = EM.46,
         neuron_46 = EM.47)
  
em <- clean_names(em)
```

### changing variable types

```{r}
bm <-
  bm %>%
  mutate(odor_1 = as.integer(odor_1),
         odor_2 = as.integer(odor_2),
         odor_3 = as.integer(odor_3),
         odor_4 = as.integer(odor_4),
         odor_5 = as.integer(odor_5),
         position_1 = as.integer(position_1),
         position_2 = as.integer(position_2),
         position_3 = as.integer(position_3),
         position_4 = as.integer(position_4),
         position_5 = as.integer(position_5),
         in_seq_log = as.integer(in_seq_log),
         performance_log = as.integer(performance_log),
         poke_events = as.integer(poke_events),
         front_reward = as.integer(front_reward),
         back_reward = as.integer(back_reward))
glimpse(bm)
```

# Adding Trial Column in Behavior Matrix

```{r}
# Focus on time_bin and poke_events variables in the bm data frame
# Filter when the rat pokes in and pokes out (trial starts and ends)
# Convert all -1s in poke_events column to 1s
# Every 2 rows represents the start of a trial and the end of a trial
# Taking the ceiling of the cumulative sum of poke_event divided by 2 gives us the appropriate trial number for every two rows
bm_trials <- bm %>% 
  select(time_bin, poke_events) %>% 
  filter(poke_events != 0) %>% 
  mutate(poke_events = case_when(poke_events != 0 ~ 1,
                                 poke_events == 0 ~ 0)) %>% 
  mutate(trial = as.integer(ceiling(cumsum(poke_events) / 2))) %>% 
  select(time_bin, trial) 

# merging the trial column with the original bm data frame
# trials column will now have NAs when time_bin has no overlap
bm <- bm %>% 
  left_join(bm_trials, by = c("time_bin")) 
  
# making sure there are 240 trials
bm_trials %>% 
  tail()

# Filling in gaps between trial start and trial end
# The reamining NAs should just be 0 (trial 0 == dead period)
bm <- bm %>% 
  mutate(trial = runner::fill_run(trial, only_within = TRUE)) %>% 
  replace_na(list(trial = 0))
```

# Merging Trials and Time with Ensemble Matrix (Neurons)

```{r}
# merging the following variables with the ensemble matrix storing the neurons firing activity
em_trials <- bm %>% 
  select(time_bin, trial, odor_1, odor_2, odor_3, odor_4, odor_5) %>% 
  cbind(em) 
```

# Logistic Regression Model

### Creating Odor Column (Response) Variable

```{r}
odor_1_trials <- em_trials %>% 
  filter(odor_1 == 1) %>% 
  select(trial) %>% 
  pull()

odor_2_trials <- em_trials %>% 
  filter(odor_2 == 1) %>% 
  select(trial) %>% 
  pull()

odor_3_trials <- em_trials %>% 
  filter(odor_3 == 1) %>% 
  select(trial) %>% 
  pull()

odor_4_trials <- em_trials %>% 
  filter(odor_4 == 1) %>% 
  select(trial) %>% 
  pull()

odor_5_trials <- em_trials %>% 
  filter(odor_5 == 1) %>% 
  select(trial) %>% 
  pull()
```


```{r}
em_trials_odors <- em_trials %>% 
  filter(trial != 0) %>% 
  mutate(
    odor_1 = case_when(
      trial %in% odor_1_trials ~ 1,
      !(trial %in% odor_1_trials) ~ 0),
    odor_2 = case_when(
      trial %in% odor_2_trials ~ 1,
      !(trial %in% odor_2_trials) ~ 0),
    odor_3 = case_when(
      trial %in% odor_3_trials ~ 1,
      !(trial %in% odor_3_trials) ~ 0),
    odor_4 = case_when(
      trial %in% odor_4_trials ~ 1,
      !(trial %in% odor_4_trials) ~ 0),
    odor_5 = case_when(
      trial %in% odor_5_trials ~ 1,
      !(trial %in% odor_5_trials) ~ 0)
  ) %>% 
  mutate(odor = case_when(
    odor_1 == 1 ~ 1,
    odor_2 == 1 ~ 2,
    odor_3 == 1 ~ 3,
    odor_4 == 1 ~ 4,
    odor_5 == 1 ~ 5,
  )) 



train <- em_trials_odors %>% 
  group_by(trial) %>% 
  slice(250:500) %>% 
  summarise(across(neuron_1:neuron_46, sum)) %>% 
  mutate(odor = case_when(
    trial %in% odor_1_trials ~ 1,
    trial %in% odor_2_trials ~ 2,
    trial %in% odor_3_trials ~ 3,
    trial %in% odor_4_trials ~ 4,
    trial %in% odor_5_trials ~ 5
  )) 
  
test <- em_trials_odors %>% 
  group_by(trial) %>% 
  slice(-(250:500)) %>% 
  summarise(across(neuron_1:neuron_46, sum)) %>% 
  mutate(odor = case_when(
    trial %in% odor_1_trials ~ 1,
    trial %in% odor_2_trials ~ 2,
    trial %in% odor_3_trials ~ 3,
    trial %in% odor_4_trials ~ 4,
    trial %in% odor_5_trials ~ 5
  )) 
```

__Potential Predictors (Neurons): 4, 5, 6, 12, 13, 14, 16, 17, 18, , 27, 34, 35, 40, 42, 44, 45__


### Predicting Odor A or Not Odor A 
```{r}
set.seed(1738)
ctrl <- trainControl(method = 'cv', number = 10)
model_1 <- train(odor~., data = odor_a_test, method = 'glm', family = binomial(link = "logit"),  trControl = ctrl)
print(model_1)
summary(model_1)

predicted <- predict(model, test, type="response")

set.seed(1)
sample <- sample(c(TRUE, FALSE), nrow(odor_a_test), replace=TRUE, prob=c(0.7,0.3))
train_1 <- odor_a_test[sample, ]
test_1 <- odor_a_test[!sample, ]



nshuffle = 50
for (j in 0:nshuffle){
  set.seed(100+nshuffle)
  ctrl <- trainControl(method = 'cv', number = 10)
  model_1 <- train(odor~., data = , method = 'lm', trControl = ctrl)
}
model_1[nshuffle] <- train(odor~., data = , method = 'lm' , trControl = ctrl)




```


```{r}
odor_a_train <- train %>% 
  mutate(odor = case_when(
    odor == 1 ~ 1, 
    odor != 1 ~ 0
  )) %>% 
  select(where(~any(. != 0)))

odor_a_test <- test %>% 
  mutate(odor = case_when(
    odor == 1 ~ 1, 
    odor != 1 ~ 0
  ))

odor_a_test <- subset(odor_a_test, select = -c(trial))

m1 <- glm(odor ~.,
          family = binomial(link = "logit"), 
          data = odor_a_train)
summary(m1)

percentage = 0
count = 0
#for (i in 1:10) {
 # percentage = percentage + wassup[i]
  #count = count + 1
#}
print(percentage)
print(count)

predict.fit = m1 %>%  
  predict(odor_a_test, type="response") # pipe operator run model on train and then run on test data
head(predict.fit)
length(predict.fit)
predicted.classes <- ifelse(predict.fit > 0.5, 1,0)

pca <- prcomp(odor_a_train[,c(2:43)], center = TRUE,scale. = TRUE)
summary(pca)

counter=0
for(i in 1:nrow(odor_a_test))
{
  if(predicted.classes[i] != odor_a_test$odor[i])
  {counter=counter+1}
}
# prediction not equal to actual gender
# if I predicted a 1 as 0 then I misclassified
counter
misclassification.rate=counter/nrow(odor_a_test)
misclassification.rate

```




### Predicting Odor B or Not Odor B

```{r}
odor_b_train <- train %>% 
  mutate(odor = case_when(
    odor == 2 ~ 1, 
    odor != 2 ~ 0
  )) %>% 
  select(where(~any(. != 0)))

odor_b_test <- test %>% 
  mutate(odor = case_when(
    odor == 2 ~ 1, 
    odor != 2 ~ 0
  ))

m2 <- glm(odor ~ neuron_12 + neuron_13 + neuron_14 + neuron_16 + 
            neuron_17 + neuron_18 + neuron_4 + neuron_5 + neuron_6 + 
            neuron_27 + neuron_34 + neuron_35 + neuron_40 + neuron_42 + neuron_44 + neuron_45,
          family = binomial(link = "logit"), 
          data = odor_b_train)
summary(m2)

predict.fit = m2 %>%  predict(odor_b_test,type="response") # pipe operator run model on train and then run on test data
head(predict.fit)
length(predict.fit)
predicted.classes <- ifelse(predict.fit > 0.5, 1,0) # if in the predict fit data set if the number is greater than 0.5 then it is a 1 otherwise it is a 0 

counter=0
for(i in 1:nrow(odor_b_test))
{
  if(predicted.classes[i] != odor_b_test$odor[i])
  {counter=counter+1}
}
# prediction not equal to actual gender
# if I predicted a 1 as 0 then I misclassified
counter
misclassification.rate=counter/nrow(odor_b_test)
misclassification.rate
```


### Predicting Odor C or Not Odor C

```{r}
odor_c_train <- train %>% 
  mutate(odor = case_when(
    odor == 3 ~ 1, 
    odor != 3 ~ 0
  )) %>% 
  select(where(~any(. != 0)))

odor_c_test <- test %>% 
  mutate(odor = case_when(
    odor == 3 ~ 1, 
    odor != 3 ~ 0
  ))

m3 <- glm(odor ~ neuron_1 + neuron_2 + neuron_4 + neuron_5 + neuron_6 + neuron_7 + neuron_8 + neuron_9 + neuron_10 + neuron_11 + neuron_12 + neuron_13 + neuron_14 + neuron_15 + neuron_16 + neuron_17 + neuron_18 + neuron_19 + neuron_20 + neuron_24 + neuron_25 + neuron_26 + neuron_27 + neuron_28 + neuron_29 + neuron_30 + neuron_31 + neuron_32 + neuron_33 + neuron_34 + neuron_35 + neuron_36 + neuron_37 + neuron_38 + neuron_39 + neuron_40 + neuron_41 + neuron_42 + neuron_44 + neuron_45 + neuron_46,
          family = binomial(link = "logit"), 
          data = odor_c_train)
summary(m3)



predict.fit = m3 %>%  
  predict(odor_c_test, type="response") # pipe operator run model on train and then run on test data
head(predict.fit)
length(predict.fit)
predicted.classes <- ifelse(predict.fit > 0.5, 1,0)
#prcomp(odor_a_train[,c(2:43)], center = TRUE,scale. = TRUE)

counter=0
for(i in 1:nrow(odor_c_test))
{
  if(predicted.classes[i] != odor_c_test$odor[i])
  {counter=counter+1}
}
# prediction not equal to actual gender
# if I predicted a 1 as 0 then I misclassified
counter
misclassification.rate=counter/nrow(odor_c_test)
misclassification.rate

```

### Predicting Odor D or Not Odor D

```{r}
odor_d_train <- train %>% 
  mutate(odor = case_when(
    odor == 4 ~ 1, 
    odor != 4 ~ 0
  )) %>% 
  select(where(~any(. != 0)))

odor_d_test <- test %>% 
  mutate(odor = case_when(
    odor == 4 ~ 1, 
    odor != 4 ~ 0
  ))

m4 <- glm(odor ~ neuron_1 + neuron_2 + neuron_4 + neuron_5 + neuron_6 + neuron_7 + neuron_8 + neuron_9 + neuron_10 + neuron_11 + neuron_12 + neuron_13 + neuron_14 + neuron_15 + neuron_16 + neuron_17 + neuron_18 + neuron_19 + neuron_20 + neuron_24 + neuron_25 + neuron_26 + neuron_27 + neuron_28 + neuron_29 + neuron_30 + neuron_31 + neuron_32 + neuron_33 + neuron_34 + neuron_35 + neuron_36 + neuron_37 + neuron_38 + neuron_39 + neuron_40 + neuron_41 + neuron_42 + neuron_44 + neuron_45 + neuron_46,
          family = binomial(link = "logit"), 
          data = odor_d_train)
summary(m4)



predict.fit = m4 %>%  
  predict(odor_d_test, type="response") # pipe operator run model on train and then run on test data
head(predict.fit)
length(predict.fit)
predicted.classes <- ifelse(predict.fit > 0.5, 1,0)
#prcomp(odor_a_train[,c(2:43)], center = TRUE,scale. = TRUE)

counter=0
for(i in 1:nrow(odor_d_test))
{
  if(predicted.classes[i] != odor_d_test$odor[i])
  {counter=counter+1}
}
# prediction not equal to actual gender
# if I predicted a 1 as 0 then I misclassified
counter
misclassification.rate=counter/nrow(odor_d_test)
misclassification.rate

```

### Predicting Odor E or Not Odor E

```{r}
odor_e_train <- train %>% 
  mutate(odor = case_when(
    odor == 5 ~ 1, 
    odor != 5 ~ 0
  )) %>% 
  select(where(~any(. != 0)))

odor_e_test <- test %>% 
  mutate(odor = case_when(
    odor == 5 ~ 1, 
    odor != 5 ~ 0
  ))

m5 <- glm(odor ~ neuron_1 + neuron_2 + neuron_4 + neuron_5 + neuron_6 + neuron_7 + neuron_8 + neuron_9 + neuron_10 + neuron_11 + neuron_12 + neuron_13 + neuron_14 + neuron_15 + neuron_16 + neuron_17 + neuron_18 + neuron_19 + neuron_20 + neuron_24 + neuron_25 + neuron_26 + neuron_27 + neuron_28 + neuron_29 + neuron_30 + neuron_31 + neuron_32 + neuron_33 + neuron_34 + neuron_35 + neuron_36 + neuron_37 + neuron_38 + neuron_39 + neuron_40 + neuron_41 + neuron_42 + neuron_44 + neuron_45 + neuron_46,
          family = binomial(link = "logit"), 
          data = odor_e_train)
summary(m5)

predict.fit = m5 %>%  predict(odor_e_test,type="response") # pipe operator run model on train and then run on test data
head(predict.fit)
length(predict.fit)
predicted.classes <- ifelse(predict.fit > 0.5, 1,0) # if in the predict fit data set if the number is greater than 0.5 then it is a 1 otherwise it is a 0 

counter=0
for(i in 1:nrow(odor_e_test))
{
  if(predicted.classes[i] != odor_e_test$odor[i])
  {counter=counter+1}
}
# prediction not equal to actual gender
# if I predicted a 1 as 0 then I misclassified
counter
misclassification.rate=counter/nrow(odor_e_test)
misclassification.rate
```

# making vectors for the entire column of each Neuron
# making a vector for the firing count of each neuron


