---
title: "Week 3 Report Part 2"
author: "Giles Carlos, Mia Chiu, Alyssandrei Parinas, Cadence Pinkerton, James Owens"
date: '2022-07-12'
output: html_document
---

# Libraries

```{r}
#install.packages("runner")
library(tidyverse)
library(R.matlab)
library(janitor)
library(readr)
library(dplyr)
library(runner)
library(gridExtra)
library(caret)
library(InformationValue)
library(ISLR)
```

# Loading in Data

```{r}
behavior_m <- readMat(here::here("data/superchris_BM.mat"))
ensemble_m <- readMat(here::here("data/superchris_EM_onlyspikes_c.mat"))
```

# Cleaning Data

### Pulling from List

```{r}
em <- data.frame(ensemble_m[1])
bm <- data.frame(behavior_m[1]) 
col_names <- data.frame(behavior_m[2])
```

### Renaming variables 

```{r}
bm <-
  bm %>%
  rename(time_bin = behavMatrix.1,
         odor_1 = behavMatrix.2,
         odor_2 = behavMatrix.3,
         odor_3 = behavMatrix.4,
         odor_4 = behavMatrix.5,
         odor_5 = behavMatrix.6,
         position_1 = behavMatrix.7,
         position_2 = behavMatrix.8,
         position_3 = behavMatrix.9,
         position_4 = behavMatrix.10,
         position_5 = behavMatrix.11,
         in_seq_log = behavMatrix.12,
         performance_log = behavMatrix.13,
         poke_events = behavMatrix.14,
         front_reward = behavMatrix.15,
         back_reward = behavMatrix.16,
         x_val_pos = behavMatrix.17,
         y_val_pos = behavMatrix.18)
  
bm <- clean_names(bm)
  
em <- subset(em, select = -c(EM.1) )

em <- 
  em %>%
  rename(neuron_1 = EM.2,
         neuron_2 = EM.3,
         neuron_3 = EM.4,
         neuron_4 = EM.5,
         neuron_5 = EM.6,
         neuron_6 = EM.7,
         neuron_7 = EM.8,
         neuron_8 = EM.9,
         neuron_9 = EM.10,
         neuron_10 = EM.11,
         neuron_11 = EM.12,
         neuron_12 = EM.13,
         neuron_13 = EM.14,
         neuron_14 = EM.15,
         neuron_15 = EM.16,
         neuron_16 = EM.17,
         neuron_17 = EM.18,
         neuron_18 = EM.19,
         neuron_19 = EM.20,
         neuron_20 = EM.21,
         neuron_21 = EM.22,
         neuron_22 = EM.23,
         neuron_23 = EM.24,
         neuron_24 = EM.25,
         neuron_25 = EM.26,
         neuron_26 = EM.27,
         neuron_27 = EM.28,
         neuron_28 = EM.29,
         neuron_29 = EM.30,
         neuron_30 = EM.31,
         neuron_31 = EM.32,
         neuron_32 = EM.33,
         neuron_33 = EM.34,
         neuron_34 = EM.35,
         neuron_35 = EM.36,
         neuron_36 = EM.37,
         neuron_37 = EM.38,
         neuron_38 = EM.39,
         neuron_39 = EM.40,
         neuron_40 = EM.41,
         neuron_41 = EM.42,
         neuron_42 = EM.43,
         neuron_43 = EM.44,
         neuron_44 = EM.45,
         neuron_45 = EM.46,
         neuron_46 = EM.47)
  
em <- clean_names(em)
```

### changing variable types

```{r}
bm <-
  bm %>%
  mutate(odor_1 = as.integer(odor_1),
         odor_2 = as.integer(odor_2),
         odor_3 = as.integer(odor_3),
         odor_4 = as.integer(odor_4),
         odor_5 = as.integer(odor_5),
         position_1 = as.integer(position_1),
         position_2 = as.integer(position_2),
         position_3 = as.integer(position_3),
         position_4 = as.integer(position_4),
         position_5 = as.integer(position_5),
         in_seq_log = as.integer(in_seq_log),
         performance_log = as.integer(performance_log),
         poke_events = as.integer(poke_events),
         front_reward = as.integer(front_reward),
         back_reward = as.integer(back_reward))
glimpse(bm)
```

# Adding Trial Column in Behavior Matrix

```{r}
# Focus on time_bin and poke_events variables in the bm data frame
# Filter when the rat pokes in and pokes out (trial starts and ends)
# Convert all -1s in poke_events column to 1s
# Every 2 rows represents the start of a trial and the end of a trial
# Taking the ceiling of the cumulative sum of poke_event divided by 2 gives us the appropriate trial number for every two rows
bm_trials <- bm %>% 
  select(time_bin, poke_events) %>% 
  filter(poke_events != 0) %>% 
  mutate(poke_events = case_when(poke_events != 0 ~ 1,
                                 poke_events == 0 ~ 0)) %>% 
  mutate(trial = as.integer(ceiling(cumsum(poke_events) / 2))) %>% 
  select(time_bin, trial) 

# merging the trial column with the original bm data frame
# trials column will now have NAs when time_bin has no overlap
bm <- bm %>% 
  left_join(bm_trials, by = c("time_bin")) 
  
# making sure there are 240 trials
bm_trials %>% 
  tail()

# Filling in gaps between trial start and trial end
# The reamining NAs should just be 0 (trial 0 == dead period)
bm <- bm %>% 
  mutate(trial = runner::fill_run(trial, only_within = TRUE)) %>% 
  replace_na(list(trial = 0))
```

# Merging Trials and Time with Ensemble Matrix (Neurons)

```{r}
# merging the following variables with the ensemble matrix storing the neurons firing activity
em_trials <- bm %>% 
  select(time_bin, trial, odor_1, odor_2, odor_3, odor_4, odor_5) %>% 
  cbind(em) 
```

# Logistic Regression Model

### Creating Odor Column (Response) Variable

```{r}
odor_1_trials <- em_trials %>% 
  filter(odor_1 == 1) %>% 
  select(trial) %>% 
  pull()

odor_2_trials <- em_trials %>% 
  filter(odor_2 == 1) %>% 
  select(trial) %>% 
  pull()

odor_3_trials <- em_trials %>% 
  filter(odor_3 == 1) %>% 
  select(trial) %>% 
  pull()

odor_4_trials <- em_trials %>% 
  filter(odor_4 == 1) %>% 
  select(trial) %>% 
  pull()

odor_5_trials <- em_trials %>% 
  filter(odor_5 == 1) %>% 
  select(trial) %>% 
  pull()
```


```{r}
em_trials_odors <- em_trials %>% 
  filter(trial != 0) %>% 
  mutate(
    odor_1 = case_when(
      trial %in% odor_1_trials ~ 1,
      !(trial %in% odor_1_trials) ~ 0),
    odor_2 = case_when(
      trial %in% odor_2_trials ~ 1,
      !(trial %in% odor_2_trials) ~ 0),
    odor_3 = case_when(
      trial %in% odor_3_trials ~ 1,
      !(trial %in% odor_3_trials) ~ 0),
    odor_4 = case_when(
      trial %in% odor_4_trials ~ 1,
      !(trial %in% odor_4_trials) ~ 0),
    odor_5 = case_when(
      trial %in% odor_5_trials ~ 1,
      !(trial %in% odor_5_trials) ~ 0)
  ) %>% 
  mutate(odor = case_when(
    odor_1 == 1 ~ 1,
    odor_2 == 1 ~ 2,
    odor_3 == 1 ~ 3,
    odor_4 == 1 ~ 4,
    odor_5 == 1 ~ 5,
  )) 



train <- em_trials_odors %>% 
  group_by(trial) %>% 
  slice(250:500) %>% 
  summarise(across(neuron_1:neuron_46, sum)) %>% 
  mutate(odor = case_when(
    trial %in% odor_1_trials ~ 1,
    trial %in% odor_2_trials ~ 2,
    trial %in% odor_3_trials ~ 3,
    trial %in% odor_4_trials ~ 4,
    trial %in% odor_5_trials ~ 5
  )) 
  
test <- em_trials_odors %>% 
  group_by(trial) %>% 
  slice(-(250:500)) %>% 
  summarise(across(neuron_1:neuron_46, sum)) %>% 
  mutate(odor = case_when(
    trial %in% odor_1_trials ~ 1,
    trial %in% odor_2_trials ~ 2,
    trial %in% odor_3_trials ~ 3,
    trial %in% odor_4_trials ~ 4,
    trial %in% odor_5_trials ~ 5
  )) 
```

__Potential Predictors (Neurons): 4, 5, 6, 12, 13, 14, 16, 17, 18, , 27, 34, 35, 40, 42, 44, 45__


### Predicting Odor A or Not Odor A 

```{r}
odor_a_train <- train %>% 
  mutate(odor = case_when(
    odor == 1 ~ 1, 
    odor != 1 ~ 0
  )) %>% 
  #select(where(~any(. != 0))) %>% 
  select(-trial)

odor_a_test <- test %>% 
  mutate(odor = case_when(
    odor == 1 ~ 1, 
    odor != 1 ~ 0
  )) %>%  
  #select(where(~any(. != 0))) %>% 
  select(-trial)

m1 <- glm(odor ~.,
          family = binomial(link = "logit"), 
          data = odor_a_train)
summary(m1)

predictions <- predict(m1, odor_a_test, type = "response") # run model on train and then run on test data

odor_a_pred <- data.frame(predictions_a = predict(m1, odor_a_test, type = "response")) # run model on 

odor_a_pred <- odor_a_pred %>% 
  mutate(probs_a = exp(predictions_a)/(1+exp(predictions_a))) 

optimal <- optimalCutoff(odor_a_test$odor, odor_a_pred$probs_a)
# optimal = 0.009

odor_a_pred <- odor_a_pred %>% 
  mutate(pred_a = ifelse(probs_a > 0.501, "A", "Not A"))
# glm_pred <- predictions %>%
  # mutate(pred = ifelse(probs>.5, "E", "Not E"))

odor_a_pred <- cbind(odor_a_test$odor, odor_a_pred) %>% 
  rename(actual_odor_a = `odor_a_test$odor`)


#optimal <- optimalCutoff(odor_a_test$odor, predictions)[1]

#confusionMatrix(odor_a_test$odor, predictions)

#optimal <- optimalCutoff(odor_a_test$odor, predictions)[1]

#confusionMatrix(odor_a_test$odor, predictions)



```

```{r}
# PRINCIPAL COMPONENT ANALYSIS
pca <- prcomp(odor_a_train[,c(2, 4:20, 24:43)], center = TRUE,scale. = TRUE)
summary(pca)

percentage = 0
count = 0
#for (i in 1:10) {
 # percentage = percentage + wassup[i]
  #count = count + 1
#}
print(percentage)
print(count)
```



```{r}

set.seed(107)
inTrain <- createDataPartition(
  y = odor_a_test$odor,  ## the outcome data are needed
  p = .75, ## The percentage of data in the training set
  list = FALSE
)
str(inTrain)
training <- odor_a_test[ inTrain,]
testing  <- odor_a_test[-inTrain,]
nrow(training) # 180
nrow(testing) # 60

model_1 <- train(odor~., 
                 data = training, 
                 method = 'glm', 
                 family = "binomial",  
                 trControl = ctrl)
print(model_1)
summary(model_1)

predicted <- predict(model_1, testing)

set.seed(1)
sample <- sample(c(TRUE, FALSE), nrow(odor_a_test), replace=TRUE, prob=c(0.7,0.3))
train_1 <- odor_a_test[sample, ]
test_1 <- odor_a_test[!sample, ]



nshuffle = 50
for (j in 0:nshuffle){
  set.seed(100+nshuffle)
  ctrl <- trainControl(method = 'cv', number = 10)
  model_1 <- train(odor~., data = , method = 'lm', trControl = ctrl)
}
model_1[nshuffle] <- train(odor~., data = , method = 'lm' , trControl = ctrl)

```

### Predicting Odor B or Not Odor B

```{r}
odor_b_train <- train %>% 
  mutate(odor = case_when(
    odor == 2 ~ 1, 
    odor != 2 ~ 0
  )) %>% 
  select(where(~any(. != 0)))

odor_b_test <- test %>% 
  mutate(odor = case_when(
    odor == 2 ~ 1, 
    odor != 2 ~ 0
  ))

m2 <- glm(odor ~ .,
          family = binomial(link = "logit"), 
          data = odor_b_train)
summary(m2)

odor_b_pred <- data.frame(predictions_b = predict(m2, odor_b_test, type = "response")) # run model on 

odor_b_pred <- odor_b_pred %>% 
  mutate(probs_b = exp(predictions_b)/(1+exp(predictions_b))) 

optimal <- optimalCutoff(odor_b_test$odor, odor_b_pred$probs_b)
# optimal = 0.721

odor_b_pred <- odor_b_pred %>% 
  mutate(pred_b = ifelse(probs_b > 0.721, "B", "Not B"))
# glm_pred <- predictions %>%
  # mutate(pred = ifelse(probs>.5, "E", "Not E"))

odor_b_pred <- cbind(odor_b_test$odor, odor_b_pred) %>% 
  rename(actual_odor_b = `odor_b_test$odor`)
optimal <- optimalCutoff(odor_b_test$odor, predictions)[1]

confusionMatrix(odor_b_test$odor, predictions)
```


### Predicting Odor C or Not Odor C

```{r}
odor_c_train <- train %>% 
  mutate(odor = case_when(
    odor == 3 ~ 1, 
    odor != 3 ~ 0
  )) %>% 
  select(where(~any(. != 0)))

odor_c_test <- test %>% 
  mutate(odor = case_when(
    odor == 3 ~ 1, 
    odor != 3 ~ 0
  ))

m3 <- glm(odor ~ .,
          family = binomial(link = "logit"), 
          data = odor_c_train)
summary(m3)

odor_c_pred <- data.frame(predictions_c = predict(m3, odor_c_test, type = "response")) # run model on 

odor_c_pred <- odor_c_pred %>% 
  mutate(probs_c = exp(predictions_c)/(1+exp(predictions_c))) 

optimal <- optimalCutoff(odor_c_test$odor, odor_c_pred$probs_c)
# optimal = 0.7310586

odor_c_pred <- odor_c_pred %>% 
  mutate(pred_c = ifelse(probs_c > .731, "C", "Not C"))
# glm_pred <- predictions %>%
  # mutate(pred = ifelse(probs>.5, "C", "Not C"))

odor_c_pred <- cbind(odor_c_test$odor, odor_c_pred) %>% 
  rename(actual_odor_c = `odor_c_test$odor`)

confusionMatrix(odor_c_test$odor, predictions)

```

### Predicting Odor D or Not Odor D

```{r}
odor_d_train <- train %>% 
  mutate(odor = case_when(
    odor == 4 ~ 1, 
    odor != 4 ~ 0
  )) %>% 
  #select(where(~any(. != 0)))
  select(-trial)
  
odor_d_test <- test %>% 
  mutate(odor = case_when(
    odor == 4 ~ 1, 
    odor != 4 ~ 0
  )) %>% 
  select(-trial)
  

m4 <- glm(odor ~ .,
          family = binomial(link = "logit"), 
          data = odor_d_train)
summary(m4)

odor_d_pred <- data.frame(predictions_d = predict(m4, odor_d_test, type = "response")) # run model on 

odor_d_pred <- odor_d_pred %>% 
  mutate(probs_d = exp(predictions_d)/(1+exp(predictions_d))) 

optimal <- optimalCutoff(odor_d_test$odor, odor_d_pred$probs_d)
# optimal = 0.7310586

odor_d_pred <- odor_d_pred %>% 
  mutate(pred_d = ifelse(probs_d > .60, "D", "Not D"))
# glm_pred <- predictions %>%
  # mutate(pred = ifelse(probs>.5, "E", "Not E"))

odor_d_pred <- cbind(odor_d_test$odor, odor_d_pred) %>% 
  rename(actual_odor_d = `odor_d_test$odor`)

confusionMatrix(odor_d_test$odor, predictions)

```

### Predicting Odor E or Not Odor E

```{r}
odor_e_train <- train %>% 
  mutate(odor = case_when(
    odor == 5 ~ 1, 
    odor != 5 ~ 0
  )) %>% 
  select(where(~any(. != 0)))

odor_e_test <- test %>% 
  mutate(odor = case_when(
    odor == 5 ~ 1, 
    odor != 5 ~ 0
  ))

m5 <- glm(odor ~ .,
          family = binomial(link = "logit"), 
          data = odor_e_train)
summary(m5)

odor_e_pred <- data.frame(predictions_e = predict(m5, odor_e_test, type = "response")) # run model on 

odor_e_pred <- odor_e_pred %>% 
  mutate(probs_e = exp(predictions_e)/(1+exp(predictions_e))) 

optimal <- optimalCutoff(odor_e_test$odor, odor_e_pred$probs_e)
# optimal = 0.7310586

odor_e_pred <- odor_e_pred %>% 
  mutate(pred_e = ifelse(probs_e > .70, "E", "Not E"))
# glm_pred <- predictions %>%
  # mutate(pred = ifelse(probs>.5, "E", "Not E"))

odor_e_pred <- cbind(odor_e_test$odor, odor_e_pred) %>% 
  rename(actual_odor_e = `odor_e_test$odor`)
optimal <- optimalCutoff(odor_e_test$odor, predictions)[1]

confusionMatrix(odor_e_test$odor, predictions)

```

## Combining
```{r}
combined_pred <- cbind(odor_a_pred, 
                       odor_b_pred, 
                       odor_c_pred, 
                       odor_d_pred, 
                       odor_e_pred)

combined_pred <- combined_pred %>% 
  select(probs_a, probs_b, probs_c, probs_d, probs_e, 
         pred_a, pred_b, pred_c, pred_d, pred_e, 
         actual_odor_a, actual_odor_b, actual_odor_c, actual_odor_d, actual_odor_e) %>% 
  rowwise() %>% 
  mutate(max_prob = max(c(probs_a, probs_b, probs_c, probs_d, probs_e))) %>% 
  mutate(pred_odor = case_when(
    probs_a == max_prob & pred_a == "A" ~ 1,
    probs_a == max_prob & pred_a == "Not A" ~ 0,
    probs_b == max_prob & pred_b == "B" ~ 2,
    probs_b == max_prob & pred_b == "Not B" ~ 0,
    probs_c == max_prob & pred_c == "C" ~ 3,
    probs_c == max_prob & pred_c == "Not C" ~ 0,
    probs_d == max_prob & pred_d == "D" ~ 4,
    probs_d == max_prob & pred_d == "Not D" ~ 0,
    probs_e == max_prob & pred_e == "E" ~ 5,
    probs_e == max_prob & pred_e == "Not E" ~ 0,
  )) %>% 
  mutate(actual_odor = case_when(
    actual_odor_a == 1 ~ 1,
    actual_odor_b == 1 ~ 2,
    actual_odor_c == 1 ~ 3,
    actual_odor_d == 1 ~ 4,
    actual_odor_e == 1 ~ 5
  )) 
  
confusionMatrix(combined_pred$actual_odor, combined_pred$pred_odor)

```


# making vectors for the entire column of each Neuron
# making a vector for the firing count of each neuron


